### 2022-07-08 preprint.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@7dfa55f42d368132ed2c1af3d1475ee71992276e 🚀

\textbf{Abstract}:\,Range maps are a useful tool to describe the spatial
distribution of species. However, they often need to be used with
caution, as they essentially represent a rough approximation of a
species' suitable habitats. When stacked together, the resulting
communities in each grid cell may not always be realistic, especially
when species interactions are taken into account. Here we show the
extent of the mismatch between range maps, provided by the International
Union for Conservation of Nature, and species interactions data. More
precisely, we show that local networks built from those stacked range
maps often yield unrealistic communities, where species of higher
trophic levels are completely disconnected from primary producers. We
use the well-described Serengeti food web of mammals and plants as our
case study, and provide updated range maps that take into account
food-web structure. In our analysis, most predator ranges were
restricted by the absence of herbivores. This restriction was sometimes
contradicted by GBIF occurrences, suggesting the mismatch can be due
either to the lack of information about ecological interactions or about
the geographical occurrence of preys. We finally discuss general
guidelines to help identify defective data among distributions and
interactions data, and we recommend this method as a valuable way to
assess weather the occurrence data that are being used, even if
incomplete, is ecologically accurate.

@@

Here we demonstrated how we can detect uncertainty in species
distribution data using ecological interactions. Knowing where
questionable occurrence data are can be crucial in ecological modelling
(Hortal 2008; Ladle and Hortal 2013), and accounting for these errors
can improve model outputs by diminishing the error propagation (Draper
1995). For instance, we believe this is a way to account for ecological
interactions in habitat suitability models without making the models
more complex, but making sure (not assuming) that the input data - the
species occurrence - actually accounts for ecological interactions. It
is important to notice, however, that the quality and usefulness of this
method is highly correlated with the amount and quality of data
available about species' occurrences \textbf{and} interactions. With
this paper we hope to add to the collective effort to decode the
encrypted message that is the occurrence of a species in space and time.
A promising avenue that adds to our method is the prediction of networks
and interactions in large scales (Strydom et al. 2021), for they can add
valuable information about ecological interactions where they are
missing. Additionally, in order to achieve a robust modelling framework
towards actual species distribution models we should invest in efforts
to collect and combine open data on species occurrence and interactions,
especially because we may be losing ecological interactions at least as
fast as we are losing species (Valiente-Banuet et al. 2015).

>>>>

\textbf{Abstract}:\,\textbf{Background.} Range maps are a useful tool to
describe the spatial distribution of species. However, they need to be
used with caution, as they essentially represent a rough approximation
of a species' suitable habitats. When stacked together, the resulting
communities in each grid cell may not always be realistic, especially
when species interactions are taken into account. Here we show the
extent of the mismatch between range maps, provided by the International
Union for Conservation of Nature (IUCN), and species interactions data.
More precisely, we show that local networks built from those stacked
range maps often yield unrealistic communities, where species of higher
trophic levels are completely disconnected from primary producers.
\textbf{Methodology.} We used the well-described Serengeti food web of
mammals and plants as our case study, and provide updated range maps for
all predators by taking into account food-web structure. We then used
occurrence data from the Global Biodiversity Information Facility (GBIF)
to investigate where data is most lacking. \textbf{Results.} We found
that most predator ranges comprised large areas without any overlapping
distribution of their preys. However, many of these areas contained GBIF
occurrences of the predator. \textbf{Conclusions.} Our results suggest
that the mismatch between both data sources could be due either to the
lack of information about ecological interactions or the geographical
occurrence of preys. We finally discuss general guidelines to help
identify defective data among distributions and interactions data, and
we recommend this method as a valuable way to assess whether the
occurrence data that are being used, even if incomplete, are
ecologically accurate.

@@

Here we demonstrated how we can detect uncertainty in species
distribution data using ecological interactions. Knowing where
questionable occurrence data are can be crucial in ecological modelling
(Hortal 2008; Ladle and Hortal 2013), and accounting for these errors
can improve model outputs by diminishing the error propagation (Draper
1995). For instance, we believe this is a way to account for ecological
interactions in habitat suitability models without making the models
more complex, but making sure (not assuming) that the input data - the
species occurrence - actually accounts for ecological interactions. It
is important to notice, however, that the quality and usefulness of this
method are highly correlated with the amount and quality of data
available about species' occurrences \textbf{and} interactions. With
this paper we hope to add to the collective effort to decode the
encrypted message that is the occurrence of a species in space and time.
A promising avenue that adds to our method is the prediction of networks
and interactions in large scales (Strydom et al. 2021), for they can add
valuable information about ecological interactions where they are
missing. Additionally, in order to achieve a robust modelling framework
towards actual species distribution models we should invest in efforts
to collect and combine open data on species occurrence and interactions,
especially because we may be losing ecological interactions at least as
fast as we are losing species (Valiente-Banuet et al. 2015).
